BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-09 tex/4-techniques.tex
Remove TODO on ML details.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts. To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a simple machine learning algorithm.
%
Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as \emph{download priorities} to decide the best URL to visit next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data will then be taken into account during future predictions.
%
This mechanism has shown to be mandatory for blogs hosting on a single domain a large number of non-blog web pages, such as a forum or a wiki.

\TODO{Give more details: this function implements a string score predictor using a the Distance-Weighted k-Nearest-Neighbor classifier, as described in \cite{dudani1976} http://ieeexplore.ieee.org/xpls/abs\_all.jsp?arnumber=5408784 This predictor can be used as an active machine learning algorithm by feeding it little by little with new url/score as they are discovered.}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind \cite{thereactivemanifesto2013}. The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

>>>>

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts. To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities of new URLs are determined by a machine learning system.

% Distance-Weighted k-Nearest-Neighbor
The idea is to give a high priority to URLs which are believed to point to pages with links to blog post. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. To *lighten* our explanations we first introduce the following notation: let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Each time a page is downloaded, it's URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. The value of $L(v)$ is estimated by doing a weighted average on the values of the $k$ URLs most similar to $v$.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}. The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

\TODO{To achieve this} property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.
